CS222 Project Proposal

### 2019-12-10 proposal/proposal.tex
Update proposal.tex

We will take the image recognition (classification) task as the example throughout the project.
At present, AdaBoost tends to be one possible solution.
However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.

@@

% zxy
\section{Related Work}
\paragraph{\textbf{Ensemble method}} 
Ensemble method solves the learning problem by combining several learners.
A few researchers have addressed the issue of combining a set of simple classifier. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.

>>>>

We will take the image recognition (classification) task as the example throughout the project.
At present, Boosting\cite{Schapire1989The} tends to be one possible solution.
However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.

@@

% zxy
\section{Related Work}
\paragraph{\textbf{Ensemble method}} 
Ensemble method solves the learning problem by combining several learners.
A few researchers have addressed the issue of combining a set of simple classifier. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
